### 2024-08-09 NN/plots_latex.tex
add ffn

@@

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/ReluTanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-28.png}
    \caption{ReluTanhFFNN - R2 vs. Number of Epochs (Hidden Size: 28)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/ReluTanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-12.png}
    \caption{ReluTanhFFNN - R2 vs. Number of Epochs (Hidden Size: 12)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/ReluTanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-20.png}
    \caption{ReluTanhFFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/ReluTanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
    \caption{ReluTanhFFNN - R2 vs. Number of Epochs (Hidden Size: 10)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/TanhReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-12.png}
    \caption{TanhReluFFNN - R2 vs. Number of Epochs (Hidden Size: 12)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/TanhReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-20.png}
    \caption{TanhReluFFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/TanhReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
    \caption{TanhReluFFNN - R2 vs. Number of Epochs (Hidden Size: 10)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/TanhReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-28.png}
    \caption{TanhReluFFNN - R2 vs. Number of Epochs (Hidden Size: 28)}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/TanhLinFFNN-R2-vs-Num-of-Epochs-HiddenSize-12.png}
    \caption{TanhLinFFNN - R2 vs. Number of Epochs (Hidden Size: 12)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/TanhLinFFNN-R2-vs-Num-of-Epochs-HiddenSize-28.png}
    \caption{TanhLinFFNN - R2 vs. Number of Epochs (Hidden Size: 28)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/TanhLinFFNN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
    \caption{TanhLinFFNN - R2 vs. Number of Epochs (Hidden Size: 10)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/TanhLinFFNN-R2-vs-Num-of-Epochs-HiddenSize-20.png}
    \caption{TanhLinFFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
\end{figure}

### 2024-08-09 NN/plots_preds_latex.tex
zz
add ffn

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots_preds/R2-99.65-GRNN-Impedance module.png}
    \caption{Prediction of Impedance module with GRNN - R-Squared: 0.97}
\end{figure}

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots_preds/R2-99.68-ReluTanhFFNN-Impedance-module.png}
    \caption{Prediction of Impedance module with ReluTanhFFNN epochs:20 - R-Squared: 1.00}
\end{figure}

### 2024-08-09 NN/tables/backward.tex
add ffn

    \begin{table*}
        \centering
        \begin{tabular}{lr}
\hline
 features                                                                                                     &    R2 \\
\hline
 flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2 & 82.69 \\
 conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2              & 62.45 \\
 flow\_rate1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2              & 81.63 \\
 flow\_rate1, conc\_nano1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2          & 73.64 \\
 flow\_rate1, conc\_nano1, Kfluid1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2              & 72.94 \\
 flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2        & 67.45 \\
 flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, conc\_nano2, Kfluid2, heat\_flux2, X\_D2              & 68.03 \\
 flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, Kfluid2, heat\_flux2, X\_D2              & 76.57 \\
 flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, heat\_flux2, X\_D2          & 38.28 \\
 flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, X\_D2              & 69.39 \\
 flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2        & 81.61 \\
\hline
\end{tabular}
        \caption{Results of Backward Feature Elimination}
        \label{backward}
    \end{table*}

>>>>

    \begin{table*}[h]
        \centering
        \begin{tabular}{lr}
\hline
 features                                                                                                                                 &    R2 \\
\hline
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp & 95.29 \\
 Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp             & 76.07 \\
 SG Coating, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp               & 76.07 \\
 SG Coating, Temp Alk Sol, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp            & 76.07 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp                     & 87.47 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp         & 92.79 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp                 & 92.1  \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Clay Conc, Cure Time (min), Cure Temp                   & 97.4  \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Cure Time (min), Cure Temp            & 55.97 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Temp                  & 53.91 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min)            & 74.51 \\
 Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Clay Conc, Cure Time (min), Cure Temp                               & 92.9  \\
 SG Coating, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Clay Conc, Cure Time (min), Cure Temp                                 & 92.9  \\
 SG Coating, Temp Alk Sol, Dip Time Alk (min), pH Sol, Hydro Time (h), Clay Conc, Cure Time (min), Cure Temp                              & 92.9  \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, pH Sol, Hydro Time (h), Clay Conc, Cure Time (min), Cure Temp                                       & 95.57 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), Hydro Time (h), Clay Conc, Cure Time (min), Cure Temp                           & 85.71 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Clay Conc, Cure Time (min), Cure Temp                                   & 97.5  \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Cure Time (min), Cure Temp                              & 43.32 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Clay Conc, Cure Temp                                    & 60.99 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Clay Conc, Cure Time (min)                              & 81    \\
 Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Clay Conc, Cure Time (min), Cure Temp                                               & 90.77 \\
 SG Coating, NaOH Wt\%, Dip Time Alk (min), pH Sol, Clay Conc, Cure Time (min), Cure Temp                                                 & 90.77 \\
 SG Coating, Temp Alk Sol, Dip Time Alk (min), pH Sol, Clay Conc, Cure Time (min), Cure Temp                                              & 90.77 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, pH Sol, Clay Conc, Cure Time (min), Cure Temp                                                       & 94.85 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), Clay Conc, Cure Time (min), Cure Temp                                           & 91.66 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Cure Time (min), Cure Temp                                              &  9.19 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Clay Conc, Cure Temp                                                    & 57.05 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Clay Conc, Cure Time (min)                                              & 73.86 \\
\hline
\end{tabular}
        \caption{Results of Backward Feature Elimination}
        \label{backward}
    \end{table*}
